---
title: "Homework"
output: html_notebook
---

```{r}
library(tidyverse)
data(msleep)
```

Explore the dataset

```{r}

names(msleep)
# 1] "name"         "genus"        "vore"         "order"       
#  [5] "conservation" "sleep_total"  "sleep_rem"    "sleep_cycle" 
#  [9] "awake"        "brainwt"      "bodywt"      
dim(msleep)
# 83 11


```

Jabberwockies sleep for around 7 hours a night, on average. Perform an appropriate statistical test to determine whether the mean sleep_total in the sampled population of animal types differs from the typical value for jabberwockies.

```{r}

msleep %>% 
  select(name, sleep_total) %>% 
  summarise(mean_sleep_total = mean(sleep_total))

# mean sleep_total in the sampled population of animal types: 10.43373	

# Jabberwockies sleep for around 7 hours

```

Perform an appropriate statistical test to determine whether omnivores sleep for significantly longer than herbivores, on average.
```{r}
msleep %>% 
  select(name, sleep_total, vore) %>% 
  group_by(vore) %>% 
  summarise(mean_sleep_total = mean(sleep_total))

# carni	10.378947			
# herbi	9.509375
```

Perform an appropriate statistical test to determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%
.
[Hint - think about creating an is_domesticated variable for the analysis]

```{r}

msleep %>% 
  select(name, conservation) %>% 
  filter(conservation == "domesticated") %>% 
  summarise(total_domesticated = n())
# 10	

msleep %>% 
  select(name, conservation) %>% 
  group_by(conservation) %>% 
  summarise(total_domesticated = n())
```

