---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)

tweets <- read_csv("data/code_clan_tweets.csv")

dim(tweets)

names(tweets)
```

```{r}
boxplot(tweets$favorite_count)

hist(tweets$favorite_count)

# get the outliers 
outliers <- boxplot(tweets$favorite_count, plot=FALSE)$out


print(outliers)

#A favourite count of 35 is not to high, I, therefore, will leave outliers inside the sample
```
Find the total number of favourited tweets (stored in favorite_count) that CodeClan tweets have got. Don’t add a tweet’s favorite_count to the total when the tweet was quoted (see the is_quote variable).
```{r}

  tweets_filtered <- filter(tweets, is_quote != TRUE) 

  sum(as.numeric(tweets_filtered$favorite_count))

```

Count the total number of likes (i.e. total of favorite_count), split by media type, and arrange them from most likes to least. Assume that any tweets without a listed media type are of type “text”.

```{r}

tweets %>% 
  group_by(media_type) %>% 
  summarise(count = n()) %>% 
  arrange(desc(count))

```

Find the mean number of characters that a CodeClan tweet contains.

```{r}
tweets %>% 
  mutate(tweet_length = str_length(text)) 
  

```


The code_clan_info.csv data file contains status_url along with other info. Load this in, and join it to the code_clan_tweets tibble, so that you have a status_url for each tweet. Decide which variable to join the tibbles on.

```{r}
tweets_info <- read_csv("data/code_clan_info.csv")

tweets_left <- left_join(tweets, tweets_info, by = "tweet_id")
```


From your new joined data, create a new tibble codeclan_hashtags containing only the tweet_id and hashtags in lowercase for analysis. Keep only those tweets with hashtags.
```{r}
codeclan_hashtags <- tweets_left %>% 
                      select(tweet_id, hashtags) %>% 
                      filter()
                        
codeclan_hashtags                  
```

