---
title: "Analysis - Task3"
author: "Felipe Millacura"
date: "18/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

seabird_data <- read_csv("../clean_data/seabird_data_clean.csv")
```

## Analysis questions

### For each question where we ask for bird names, give the bird’s common name, scientific name and species abbreviation.

#### Which bird had the most individual sightings?

```{r}
seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation, count) %>% 
  filter(count == "1") %>% 
  group_by(species_abbreviation) %>% 
  summarise(sightings = n()) %>% 
  arrange(desc(sightings))

seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>% 
  filter(species_abbreviation == "DIOANTEXU PL3")
```

*The bird with most individual sightings is*

| species_abbreviation  |  sightings |  species_common_name | species_scientific_name  |
|---|---|---|---|
| DIOANTEXU PL3  | 1707	  |  Wandering albatross sensu lato PL3 |  Diomedea antipodensis / exulans PL3 |

#### Which bird had the highest total count?

```{r}

seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation, count) %>% 
  group_by(species_abbreviation) %>% 
  summarise(total_count = sum(count)) %>% 
  arrange(desc(total_count))

seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>% 
  filter(species_abbreviation == "LARBUL")

```

*The bird with the highest total count is*

| species_abbreviation  |  total |  species_common_name | species_scientific_name  |
|---|---|---|---|
| LARBUL  | 7732	  |  Black-billed gull |  	Larus bulleri |

#### Which bird had the highest total count above a latitude of -30?

```{r}
seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation, count, lat) %>% 
  filter(lat > -30 ) %>% 
  group_by(species_abbreviation) %>% 
  summarise(total_count = sum(count)) %>% 
  arrange(desc(total_count))

seabird_data %>%
  select(species_common_name_taxon_age_sex_plumage_phase, species_scientific_name_taxon_age_sex_plumage_phase, species_abbreviation) %>% 
  filter(species_abbreviation == "PUFPAC")
```

*The bird with the  highest total count above a latitude of -30 is*

| species_abbreviation  |  total |  species_common_name | species_scientific_name  |
|---|---|---|---|
| PUFPAC  | 855	  | Wedge-tailed shearwater  |  	Puffinus pacificus |

#### How many different types of birds were only ever seen in groups of 1?

```{r}



seabird_data %>%
  select(species_abbreviation, count) %>%
  group_by(species_abbreviation) %>% 
  #summarise(sightings = n()) %>% 
  arrange(desc(count))

```

#### How many penguins were seen? (Hint: there are many types of penguin)

```{r}

library(stringr)

seabird_data %>%
  select(species_abbreviation, species_common_name_taxon_age_sex_plumage_phase, count) %>%
  filter(species_common_name_taxon_age_sex_plumage_phase == str_extract("[Pp][Ee][Nn][Gg][Uu][Ii][Nn]*"))
```


