---
title: "Analysis and Documentation"
author: "Felipe Millacura"
date: "18/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

cake_ingredients <- read_csv("../clean_data/cake_ingredients_clean.csv")
```

## Analysis questions

#### Which cake has the most cocoa in it?

```{r}
cake_ingredients %>% 
  select(cake, quantity, ingredient, measure) %>% 
  filter(ingredient == "cocoa")
```

*The cake with most cocoa on it is the "One Bowl Chocolate" with 10.0 tablespoons*

#### For sponge cake, how many cups of ingredients are used in total?

```{r}
cake_ingredients %>% 
  select(cake, quantity, ingredient, measure) %>% 
  filter(cake == "Sponge") %>% 
  filter(measure == "cup") %>% 
  summarise(total_cups = sum(quantity))

```

*A total of 3.5 cups are used in the sponge cake preparation*

#### How many ingredients are measured in teaspoons?

```{r}
cake_ingredients %>% 
  select(cake, quantity, ingredient, measure) %>% 
  filter(measure == "teaspoon") %>% 
  filter(ingredient == unique(ingredient)) %>% 
  summarise(teaspoon_total = n())

```

*There are a total of 12 ingredients measured in teaspoons*

#### Which cake has the most unique ingredients?

```{r}
cake_ingredients %>% 
  select(cake, ingredient) %>% 
  group_by(cake) %>% 
  summarise(ingredient_total = n()) %>% 
  arrange(desc(ingredient_total))

```

*There are two cakes with the most quantity of unique ingredients, the "Babas au Rhum" and the "One Bowl Chocolate" cakes*

#### Which ingredients are used only once?

```{r}
cake_ingredients %>% 
  select(cake, ingredient) %>% 
  group_by(ingredient) %>% 
  summarise(total_use = n()) %>% 
  filter(total_use == 1)

```

*The ingredients used only once are:*

| ingredient | times used   |
|---|---|
| bananas  |  1 |
| cream of tartar  | 1  |
| crushed ice  | 1  |
| dried currants  | 1  |
| egg white  | 1  |
| nutmeg  | 1  |
| nuts  | 1  |
| zwiebach  | 1  |


