---
title: "Homework - 30/04/2020"
output: html_notebook
---

## Loads libraries

```{r}
library(tidyverse)
library(modelr)

# visualisation packages
library(ggiraphExtra)
library(GGally)
```


## Loads data and checks inside

```{r}
data <- read.csv("data/kc_house_data.csv")

glimpse(data)
head(data)
```

## Data wrangling



```{r}
data_trim <- data %>% 
  drop_na() %>% 
  select(-date, #352 unique values
         -id, #not needed in this case
         -sqft_living15, 
         -sqft_lot15, 
         -zipcode #we do have lat and long
         )
```

Checks waterfront

```{r}
data_trim %>% 
distinct(waterfront) #it seems ok as a logical variable

class(data_trim$waterfront)
```
Check for possible alias formation
```{r}
alias(price ~ ., data= data_trim)
```
##First predictions

Checks correlation 1
```{r}
data_trim %>%
  ggpairs()

#This didn't run probably because data is not properly prepared 
```

```{r}
data_trim %>%
  ggcorr()
```

Trying full model from alias
```{r}
mod_alias <- lm(price ~ bedrooms + bathrooms + sqft_living + sqft_lot + floors + waterfront + view + condition + grade + sqft_above + sqft_basement + yr_built + yr_renovated + lat + long, data = data_trim)

summary(mod_alias) 

#R-squared:  0.6942
#It's not a good model by itself
```

Plotting and observing alias() model

```{r}

par(mfrow = c(2, 2)) 

plot(mod_alias)
```


Starts building a better model using possible useful variables obtained from ggcorr(): price, bedrooms, bathrooms, sqft_living, grade, waterfront

```{r}
#Model | Relation | R squared

mod1a <- lm(price ~ bedrooms, data = data_trim) #0.09508
mod2a <- lm(price ~ bathrooms, data = data_trim) #0.2758
mod3a <- lm(price ~ grade, data = data_trim) #0.4455
mod4a <- lm(price ~ sqft_living, data = data_trim) #0.4929
mod5a <- lm(price ~ waterfront, data = data_trim) #0.07095

summary(mod1a)
summary(mod2a)
summary(mod3a)
summary(mod4a)
summary(mod5a)
```


