---
title: "Analysis and Task4"
author: "MillacuraFA"
date: "19/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

data_candy <- read_csv("../clean_data/candy_data_clean.csv")
```

## Analysis questions

#### What is the total number of candy ratings given across the three years. (number of candy ratings, not number of raters. Don’t count missing values)

```{r}

data_candy %>%
    select(candy, rating) %>% 
  group_by(candy) %>% 
  summarise(candy_total = n()) %>% 
  nrow()
```

*There is a total of 108 candy*

#### What was the average age of people who are going out trick or treating and the average age of people 3. not going trick or treating?

```{r}

options(scipen=999)

data_candy %>% 
  select(trick_or_treat, age) %>% 
  group_by(trick_or_treat) %>% 
  summarise(avg_age = mean(age, na.rm=TRUE))

data_candy %>% 
  select(trick_or_treat, age) %>% 
  filter(trick_or_treat == "Yes") %>% 
  arrange(desc(age))
```


#### For each of joy, despair and meh, which candy bar revived the most of these ratings?

```{r}

#JOY candy rating
data_candy %>% 
  select(candy, rating) %>% 
  filter(rating == "JOY") %>% 
  group_by(candy) %>% 
  summarise(rating_total = n()) %>% 
  arrange(desc(rating_total))

#DESPAIR candy rating

data_candy %>% 
  select(candy, rating) %>% 
  filter(rating == "DESPAIR") %>% 
  group_by(candy) %>% 
  summarise(rating_total = n()) %>% 
  arrange(desc(rating_total))
  

#MEH candy rating

data_candy %>% 
  select(candy, rating) %>% 
  filter(rating == "MEH") %>% 
  group_by(candy) %>% 
  summarise(rating_total = n()) %>% 
  arrange(desc(rating_total))
  
  
  # group_by(rating) %>% 
  # summarise(total_rating = n()) %>% 
  # arrange(desc(total_rating))
```

*The candy bars that revived the most of these ratings are: *

| Rating  |  Candy |  Total |
|---|---|---|
|  Joy |  any_full_sized_candy_bar | 2611  |
|  Despair |  broken_glow_stick | 2727  |
|  Meh | lollipops  | 1570  |

#### How many people rated Starburst as despair?

```{r}

data_candy %>% 
  select(candy, rating) %>% 
  filter(candy == "starburst") %>% 
  group_by(rating) %>% 
  summarise(total_rating = n())

```

*A total of 508 people rated starbust as despair*


### For the next three questions, count despair as -1, joy as +1 and meh as 0.

#### What was the most popular candy bar by this rating system for each gender in the dataset?

```{r}

data_candy %>% 
  select(candy, rating, gender
         ) %>% 
  mutate(rating, rating_score = #(for (rate in rating){ 
    (ifelse(rating == "JOY", 1, ifelse(rating == "DESPAIR", -1, 0)))
  #  if (rating == "JOY"){
  #     rating == 1
  #   } else if (rating == "DESPAIR") {
  #     rating == -1
  #   } else {rating == 0}
  #   )
  # #}
  ) %>% 
 filter(gender == "Male") %>% 
 group_by(candy) %>%  #I don't have the gender column!!! )=
 summarise(total_score = sum(rating_score, na.rm = TRUE)) %>% 
  arrange(desc(total_score))

data_candy %>% 
  select(candy, rating, gender
         ) %>% 
  mutate(rating, rating_score = #(for (rate in rating){ 
    (ifelse(rating == "JOY", 1, ifelse(rating == "DESPAIR", -1, 0)))
  ) %>% 
 filter(gender == "Female") %>% 
 group_by(candy) %>%  #I don't have the gender column!!! )=
 summarise(total_score = sum(rating_score, na.rm = TRUE)) %>% 
  arrange(desc(total_score))
```

| Sex  |  Candy |  Total score |
|---|---|---|
|  Female |  any_full_sized_candy_bar | 875  |
|  MAle |  any_full_sized_candy_bar | 1584  |



#### What was the most popular candy bar in each year?

```{r}

data_candy %>% 
  select(candy, year, rating) %>% 
  mutate(rating, rating_score =  (
    ifelse(rating == "JOY", 1, 
      ifelse(rating == "DESPAIR", -1, 0)
        ))) %>% 
  filter(year == "2016") %>%
  group_by(candy) %>% 
  summarise(candy_rating = sum(rating_score, na.rm = TRUE)) %>% 
  arrange(desc(candy_rating))

data_candy %>% 
  select(candy, year, rating) %>% 
  mutate(rating, rating_score =  (
    ifelse(rating == "JOY", 1, 
      ifelse(rating == "DESPAIR", -1, 0)
        ))) %>% 
  filter(year == "2017") %>%
  group_by(candy) %>% 
  summarise(candy_rating = sum(rating_score, na.rm = TRUE)) %>% 
  arrange(desc(candy_rating))
```

*In 2016 the most popular candy was "any_full_sized_candy_bar" with a score of 1037, and in 2017 also but with a score of 1542*

#### What was the most popular candy bar by this rating for people in US, Canada, UK and all other countries?


```{r}
#I don't have the countries column...
```

