---
title: "Weekend homework"
output: html_notebook
---
Write a function which multiples all numbers by 15 and adds 4.

```{r}
multiply_by_15_adds_4 <- function(x){
  x * 15 + 4
}

multiply_by_15_adds_4(1:4)
```

Write a function that returns “bird”, if the input is “goose”, “duck” or “pigeon”, and returns “not bird” for all other input.

```{r}
bird_detector <- function(x){
  if (x == "goose" | x == "duck" | x == "pigeon"){
    return("bird")
  } else return("no bird")
}

bird_detector("a_weird_bird")

bird_detector("goose")
```

Write a function which multiplies all numbers by 10. If the input isn’t a number, the function should return “Invalid input”.

```{r}
multiply_and_check <- function(x){
  if (class(x) != "numeric"){
    return("Invalid input")
  } else x * 10
}

multiply_and_check(20)

multiply_and_check("weird_number")

multiply_and_check(c(1,3,4,5))

multiply_and_check(c(1,3,4,5,"invalid"))
```

For each question provide three answers: one using ifelse(), one using recode() and one using case_when(). Discuss which approach you think is easiest for each question.

Remember to load dplyr to use recode() and case_when().

```{r}
library(dplyr)

```

For the vector below, make a new vector which is equal to “Big” every time the element of sizes is greater than 10, and equal to “Small” every time the element of sizes is less than or equal to 10.

```{r}
sizes <- c(13, 15, 10, 8, 22)

ifelse(sizes > 10, "Big", "Small")
case_when(sizes > 10 ~ "Big",
       sizes <= 10 ~ "Small")

small <- c(1:10)
big <- c(11:10000)
dplyr::recode(sizes, small = "Small", big = "Big")

```

For the vector below convert:

apple → alpaca

banana → bonobo

cherry → chipmunk

```{r}
fruit <- c("apple", "apple", "banana", "cherry", "cherry")

ifelse(fruit == "apple", "alpaca", (ifelse(fruit == "banana", "bonobo", (ifelse(fruit == "cherry", "chipmunk", fruit)))) ) 

case_when(
  fruit == "apple" ~ "alpaca",
  fruit == "banana" ~ "bonobo",
  fruit == "cherry" ~ "chipmunk"
  )
recode(fruit, "apple" = "alpaca", "banana" = "bonobo", "cherry" = "chipmunk")
```

The two vectors below show the ages at marriage of each member of a couple. The first elements of each vector correspond to the first couple, the second elements to the second couple, and so on.

Create a new vector which is equal to:

“Wife older” whenever the wife’s age is highest “Husband older” when the husband’s age is highest “Same age” when they are the same age

```{r}
library(dplyr)

wife_age <- c(29L, 30L, 36L, 31L, 22L)
husband_age <- c(28L, 35L, 32L, 31L, 29L)

ifelse(wife_age > husband_age, "Wife older", (ifelse(wife_age < husband_age, "Husband older", "Same age")))

case_when(
  wife_age > husband_age ~ "Wife older",
  wife_age < husband_age ~ "Husband older",
  wife_age == husband_age ~ "Same age"
)
difference <- sign(wife_age - husband_age)
recode(difference, "1" = "Wife older", "0" = "Same age", "-1" = "Husband older")
```

```{r}
my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)
```

Use a for loop to print out every element of my_list which is of type characte

```{r}

my_list <- list(
  4,
  "apple",
  10.5,
  c("is", "an", "apple"),
  "apple",
  c("i", "like", "apples"),
  8
)

for (element in my_list){
  if (class(element) == "character"){
    print(element)
  } 
}
```
Do the same as above, but this time use a while loop

```{r}
while (class(my_list) == "character" ) {
  print(element)
  
}
```

