---
title: "Homework 02032020"
output: html_notebook
---



Read in the state_income_data.csv file using the appropriate function.

```{r}
library(readr)
state_income <- read_csv("data/state_income_data.csv")
```


How do you specify your own column names when using read_csv()?

```{r}
state_income <- read_csv("data/state_income_data.csv", col_names = c("replaces", "columns", "names", "with", "whatever", "you", "want"))
```


Read in the cars.csv file and use the col_types() function to ensure you load in:

X1 as character
mpg, cyl, disp, hp as double
vs as logical

```{r}
cars_info <- read_csv("data/cars.csv", 
                      col_types = 
                        cols(XI = col_character(), 
                        vs = col_logical(), 
                        c("mpg", "cyl", "disp", "hp") = col_double()
                        ))
```


Read in the scotland.txt file using the appropriate function.

```{r}
scotland_info <- read_delim("data/scotland.txt", delim = ";", skip = 1)
```


How do you read text into a one element character vector?

```{r}
element <- c("trial")

element[1]
```


Read in the steam-200k-sample.csv file. Fix any problems you may encounter.

```{r}
steam_200k <- read_csv("data/steam-200k-sample.csv", skip = 4)
```


Read in the historic_eu_payments.tsv file.

```{r}
historic_eu <- read_tsv("data/historic_eu_payments.tsv")
```


How do you read lines of text into a multi-element text vector?

```{r}
multi_element <- read_file("data/something.txt")

#or if there are no columns

multi_element <- read_lines("data/something.txt")
```


Read in the africa_health_data.dta file using the appropriate method.

```{r}
library(haven)

africa_health <- read_stata("data/africa_health_data.dta")
```


Read in the JSON file from the following url: http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt

```{r}
library(jsonlite)

read_json("http://makemeanalyst.com/wp-content/uploads/2017/06/sample_json.txt")
```

