---
title: "No Homework"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(GGally)
library(tidyverse)
library(modelr)
library(yardstick)
library(caret)

titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

Data Dictionary

sex: Biological Sex, male or female
age_status: adult or child (child defined as under 16)
class : Ticket class, 1 = 1st (Upper class), 2 = 2nd (Middle Class), 3 = 3rd (Lower Class)
port_embarkation: C = Cherbourg, Q = Queenstown, S = Southampton
sibsp : number of siblings / spouses aboard the Titanic
parch: number of parents / children aboard the Titanic. Some children travelled only with a nanny, therefore parch=0 for them.
survived_flag : did they survive, 0 = No, 1 = Yes



Cleaning up the data is always the first step. Do the following:

Take only observations which have a survived flag (i.e. that aren’t missing)
Turn your important variables into factors (sex, survived, pclass, embarkation)
Create an age_status variable which groups individuals under (and including) 16 years of age into a category called “child” category and those over 16 into a category called “adult”.
Drop the NA
Drop any variables you don’t need (X1, passenger_id, name, ticket, far, cabin)

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%
# Convert to factor level
    mutate(sex = as.factor(sex), 
           age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
           survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
           port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  na.omit()
```

Question 2

Have a look at your data and create some plots to ensure you know what you’re working with before you begin. Write a summary of what you have found in your plots. Which variables do you think might be useful to predict whether or not people are going to die? Knowing this before you start is the best way to have a sanity check that your model is doing a good job.


```{r}
titanic_clean %>% 
  ggpairs()
```

```{r}
titanic_clean %>% 
  ggcorr()
```


Question 3

Now you can start to build your model. Create your testing and training set using an appropriate split. Check you have balanced sets. Write down why you chose the split you did and produce output tables to show whether or not it is balanced.

```{r}
n_data <- nrow(titanic_clean)
#create test set
test_index <- sample(1:n_data, size = n_data*0.2)

#creates test set

titanic_test <- slice(titanic_clean, test_index)

#creates training set
titanic_train <- slice(titanic_clean, -test_index)
```

Question 4

Create your decision tree to try and predict survival probability using an appropriate method, and create a decision tree plot.

```{r}
library(janitor)

titanic_test %>% 
  tabyl(survived_flag)

titanic_train %>% 
  tabyl(survived_flag)

titanic_fit <- rpart(survived_flag ~ .,
                     data = titanic_train,
                     method = "class")

```

```{r}
rpart.plot(titanic_fit, yesno = 2)
```

Question 5

Write down what this tells you, in detail. What variables are important? What does each node tell you? Who has the highest chance of surviving? Who has the lowest? Provide as much detail as you can.

```{r}
# it's of high importance whether you are a men or a woman for the survival rate, 64% of men die. From the 36% of survivors a 22% are from upper class. and from the remaining 14% of low class a 10% ambarked on port S

rpart.rules(titanic_fit, cover = TRUE)
```

Question 6

Test and add your predicitons to your data. Create a confusion matrix. Write down in detial what this tells you for this specific dataset.

```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")

titanic_test_pred %>% 
  select(survived_flag, pred)

summary(titanic_test_pred)
```

```{r}
conf_mat <- titanic_test_pred %>% 
  conf_mat(truth = survived_flag,
           estimate = pred)
```

```{r}
accuracy <- titanic_test_pred %>% 
  accuracy(truth = survived_flag, estimate = pred)
```

```{r}
confusionMatrix(titanic_test_pred$pred, titanic_test_pred$survived_flag)
```