---
title: "Homework - 28042020"
output: html_notebook
---

```{r}
library(tidyverse)
library(GGally)
library(mosaicData)
library(ggiraphExtra)
```
Load the diamonds.csv data set and undertake an initial exploration of the data.
```{r}

data <- read.csv("diamonds.csv")
```

produce result summaries of the results of various model fitting functions. The function invokes particular methods which depend on the class of the first argument.
```{r}

summary(data)
```
Scatterplots of each pair of numeric variable are drawn on the left part of the figure. Pearson correlation is displayed on the right. Variable distribution is available on the diagonal.
```{r}
data %>% ggpairs()
```
Visualize the correlation of each pair of variable as a square
```{r}
data %>% 
ggcorr()
```



drop columns x, y and z from the dataset
```{r}
data_clean <- data %>% 
  select(-x, -y, -z)
```

investigate correlations between price and the predictors

```{r}
data_clean  %>% 
  ggpairs()
```


We see a reasonably strong association between the carat value and price
```{r}
data_clean %>%
  ggplot(aes(x = carat, y = price)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```

```{r}
data_clean %>%
  ggplot(aes(y = carat, x = price, group = carat)) + 
  geom_boxplot()
```

