---
title: "Task1 - analysis"
author: "Felipe Millacura"
date: "17/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- You should then have a separate script in the documentation_and_analysis folder containing your analysis code and/or markdown documentation. This will be a .Rmd file. -->

## Analysis questions

#### Who had the longest long jump seen in the data?

```{r, warning=FALSE, message=FALSE}
library(tidyverse)


decathlon_clean <- read_csv("../clean_data/decathlon_data_clean.csv")
```

```{r}
decathlon_clean %>% 
  select(surname, event, scores) %>% 
  filter(event == "long_jump") %>% 
  arrange(desc(scores)) %>% 
  top_n(1, scores)


```


*Clay has the largest long jump scoring 7.96*



#### What was the average 100m time in each competition?

```{r}
decathlon_clean %>% 
  select(competition, event, scores) %>% 
  filter(event == "running_100m") %>% 
  group_by(competition) %>% 
  summarise(mean(scores))


```

*The average 100m time for Decastar and OlympicG was 11.18 and 10.92 respectively*

#### Who had the highest total points across both competitions?

```{r}
decathlon_clean %>% 
  select(surname, competition, event, points) %>% 
  group_by(surname) %>% 
  summarise(total_points = sum(points)) %>% 
  arrange(desc(total_points)) %>% 
  top_n(1, total_points)


```

*The highest total score accros both competitions was obtained by Sebrle, with a total score of 171100 points*

#### What was the shot-put scores for the top three competitors in each competition?

```{r}
decathlon_clean %>% 
  select(surname, event, scores, points, competition) %>% 
  group_by(competition) %>% 
  filter(event == "shot_put") %>% 
  arrange(desc(points)) %>% 
  top_n(3, points)
```

*Information for the top three scores in the shot_put event are depicted below*

| surname | event | scores | points | competition |
|---|---|---|---|---|
| sebrle | shot_put | 16.36	 | 8893 | OlympicG |
| clay  | shot_put | 15.23 |  8820 | OlympicG |
| karpov  | shot_put | 15.93 |  8725 |  OlympicG |
| sebrle  | shot_put  | 14.83  |  8217 | Decastar |
| clay  | shot_put  | 14.26  |  8122 | Decastar |
| karpov  | shot_put  | 14.77  |  8099 | Decastar |

#### What was the average points for competitors who ran the 400m in less than 50 seconds vs. those than ran 400m in more than 50 seconds?

```{r}
decathlon_clean %>% 
  select(surname, event, points, scores) %>% 
  filter(event == "running_400m") %>% 
  group_by(over_50_seconds = scores > 50) %>% 
  summarise(avg_points = mean(points))


```

*The average points for competitors that ran the 400m in less than 50 seconds was 8120.48 vs 7727.17 from the ones that ran in more than 50 seconds*

